\chapter{Introduction}
\label{chap:intro}

\section{A Little History}
\label{sec:history}

	% The current `Standard Model' of particle physics was completed in June 2012 with the announcement of the Higgs boson by the ATLAS collaboration.
	% This discovery with the final piece needed to complete the picture developed over the course of the past century beginning with the discovery of the electron in 1897.

	The Standard Model is a gauge quantum field theory describing three of the four observed fundamental forces - with the inclusion of gravity remaining elusive.
	Its local gauge structure is given by:

	\begin{equation}
		SU(3)_c\times SU(2)_L\times U(1)_Y.
		\label{eq:SMGauge}
	\end{equation}

	The subscripts on the groups are simply a convenient notation.  The `c' on $SU(3)$ indicates that it is
	the strong `colour' coupling being described.  The `L' on $SU(2)$ indicates that all right-handed states are in
	the trivial representation of the group and the `Y' on the $U(1)$ indicates that this is the hypercharge group
	and not the electromagnetic group. The $SU(3)_c$ group describes the strong nuclear force (Quantum Chromodynamics
	or QCD) and its 8 gauge generators give us the massless spin-1 gluons, $G_a^\mu(x),\ a=1,\ldots,8$, present in
	the standard model. There are three weak boson states, $W_a^\mu(s),\ a=1,\ldots,3$, associated with the $SU(2)_L$ group and
	a further one, $B^\mu(x)$, which comes from the $U(1)_Y$ group.

	The only remaining boson to complete the standard model arises from the complex scalar Higgs field whose ground state is not invariant under the action of $SU(2)_L\times U(1)_Y$.
	This field breaks the standard model gauge symmetry to

	\begin{equation}
		SU(3)_c\times U(1)_{em},
		\label{eq:SMGaugeBroken}
	\end{equation}

	\noindent where the $U(1)_{em}$ refers to the electromagnetic charge.  After this `Spontaneous Symmetry Breaking' occurs three of the four aforementioned bosons, $W_a^\mu(s)$ and $B^\mu(x)$
	acquire mass and combinations of them are physically realised as the experimentally observer electroweak boson; The massive states $W^\pm, Z^0$ and the massless photon, $\gamma$.
	The photon and the $Z^0$ bosons are of particular importance in the work that follows.

	The fundamental particle content of the Standard Model also includes fermions. These are spin-$1/2$ particles which obey the spin-statistics theorem (and
	hence the Pauli exclusion principle) and comprise, along with the gluons which binds the nucleus together, all known visible matter in the universe.
	The fermions are structured in three so-called `generations', shown in table \ref{tab:fermions} and can be further subdivided into quarks and leptons.
	Quarks are colour triplets under QCD but are also charged under the electroweak group.  The up ($u$), charm ($c$) and top ($t$) quarks have electric charge
	$+\frac{2}{3}$ while the down ($d$), strange ($s$) and bottom ($b$) quarks have $-\frac{1}{3}$.
	Leptons are singlets under $SU(3)$ and so do not couple to the strong sector.  The charged leptons $e$, $\mu$ and $\tau$ have electric charge
	$-1$ and the neutrinos are neutral.

	\begin{table}[htp!]
	\begin{center}
	\begin{tabular}{c | c | c | c}
	        & First Generation & Second Generation & Third Generation   \\ \hline
	Quarks  &  $u$, $d$        & $c$, $s$          & $t$,               \\ \hline
	Leptons &  $e$, $\nu_e$    & $\mu$, $\nu_\mu$  & $\tau$, $\nu_\tau$ \\
	\end{tabular}
	\caption{The fermion content of the standard model.}
	\label{tab:fermions}
	\end{center}
	\end{table}

\section{Thesis Outline}
\label{sec:outline}

	The aim of this thesis is to detail the importance of a certain class of perurbatively higher-order terms in events with QCD radiation in the final state.  In particular
	we will consider corrections to parton-parton collisions with a $Z^0$ or $\gamma$ in association with high energy QCD radiation in the final state.

	In chapter \ref{chap:theory} I will begin by introducing quantum chromodynamics, the theory of the strong sector in the standard model, and detail how we might use this
	to calculate physical observables (such as cross-sections and differential distributions) at hadron colliders such as the Large Hadron Collider.  I will discuss how
	these observables fall prey to divergences in QCD-like quantum field theories with massless states and mention briefly how such divergences can be handled.  I will then
	describe how the computationally expensive integrals derived in subsequent chapters may be efficiently evaluated using Monte-Carlo techniques.

	In chapter \ref{chap:HEQCD} the details of QCD in the `High Energy' limit are discussed.  After completing a few instructive calculations we will see how,
	in this limit, the traditional fixed-order perturbation theory view of calculating cross-sections fades as another subset of terms, namely the `Leading
	Logarithmic' terms in $\frac{s}{t}$, become more important.  I will discuss previous work in the High Energy limit of QCD and how this can be used to factorise
	complex parton-parton scattering amplitudes into combinations of `currents' which, when combined with gauge-invariant effective gluon emission terms can be used to
	construct approximate high-multiplicity matrix elements.

	In chapter \ref{chap:Zs} the work of the previous chapter is extended to the case where there is a massive $Z^0$ boson or an off-shell photon, $\gamma^*$,
	in the final state.  A `current' for this process is derived and the complexities arising from two separate sources of interference are explored.
	This new result for the matrix element is compared to the results obtained from a Leading Order (in the strong coupling, $\alpha_s$) generator
	\texttt{MadGraph} at the level of the matrix element squared in wide regions of phase space is seen to be in exact agreement.
	This result must then be regularised to treat the divergences discussed in chapter \ref{chap:theory} and this process is presented.
	The procedure for matching this regularised result to Leading Order results is shown and the importance of the inclusion of these
	non-resummation terms is discussed. Lastly three comparisons of the High Energy Jets Z+Jets Monte-Carlo generator to recent experimental
	studies \texttt{ATLAS} and \texttt{CMS} at the LHC are shown.

	From here we use the results of chapter \ref{chap:Zs}, and the resulting publicly available Monte Carlo package, to compare our description to
	a recent experimental prediction of the ratio of the $W^\pm$+jets rate to the $\zg$+jets rate.  Our predictions are compared against
	next-to-leading order (in $\alpha_s$) results from \texttt{NJet} and leading order results from \texttt{MadGraph}.

	In chapter \ref{chap:ttbar} we apply the massive spinor-helicity to the production of a $t\overline t$ pair in hadronic collisions.  Using the
	\texttt{PySpinor} package we calculate values for the full-mass matrix element and compare them to leading-order (in $\alpha_s$) results from
	\texttt{MadGraph}.  This is a process in which the leading logarithmic contribution starts at one order higher than in previous work and so the effects
	of the resummation are not as expected to be as crucial as in the case of chapter \ref{chap:Zs} - however at large values for the centre-of-mass energy
	(such as that a future high energy circular collider) these `next-to-leading' logarithms will once again lead to the breakdown of fixed-order
	perturbation theory.

	In chapter \ref{chap:ATLAS} we discuss the results of a lengthy study of jet production from the \texttt{ATLAS} collaboration.  This analysis was a thorough
	look at BFKL-like dynamics in proton-proton colliders and the HEJ predictions are seen to describe the data well in the regions of phase-space where
	we know the effects of our resummation become relevant.  We compare the predictions from both standalone HEJ and HEJ interfaced with \texttt{ARIADNE}, a
	parton shower based on a dipole-cascade model.  Although the interface to \texttt{ARIADNE} increases the computational complexity significantly; we see that
	the Sudakov logarithms added by significantly improve the description of data.

	In chapter \ref{chap:100TeV}, with a study of $\zg$+Jets at a centre-of-mass energy of 100TeV relevant for the discussion of
	the next wave of high energy particle physics experiments (such as any Future Circular Collider) which are of great interest to the community at large.  We see....DO THE STUDY BEFORE
	WRITING THIS!

	Finally, in chapter \ref{chap:conclusion} I summarise the results of the above chapters and provide a short outlook for future work.

